Direction-Selective Resistance to Cerebrospinal-Fluid Flow As the Generative Mechanism of Syringomyelia

### 2022-07-23 manuscript/main.tex
minor change

Video \ref{video:norm} shows the original system's response representing
the normal condition. In this state, CSF made a smooth to-and-fro movement
in the subarachnoid space with the corresponding pressure wave along the
dura and the central canal. CSF also made smooth to-and-fro movements in
the channel.

>>>>

Video \ref{video:norm} shows the original system's response representing
the normal condition. In this state, the dural tension made a smooth
gradient along the spine, whose polarity alternated along the pressure
cycle. According to this pressure gradient, CSF made a smooth to-and-fro movement
in the subarachnoid space with the corresponding pressure wave along the
dura and the central canal. CSF also made smooth to-and-fro movements in
the channel.
